My title

### 2022-03-21 outputs/paper/paper.Rmd
Add all crime-related plots

### 4 Reference\
------------------------------------------------------------------------------------------------10
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(here)

@@

\newpage
#Results
## Classification of Discrimination
The identification of discrimination could be vague and inconsistent in different regions. According to Human rights in Ontario[@humanrights], there are four forms of discrimination: direct, indirect, subtle, and adverse effect discrimination; Harassment; Poisoned environment; Systemic discrimination. Discrimination often derives from different backgrounds and identities. Based on unique combination of identities, people may be exposed to specific forms of discrimination and may experience significant personal harm. The 2014 GSS on Canadians’ Safety and Security (Victimization) mainly captured gender, disability, and ethnicity. It also provides information of the condition when discrimination happens. According to Figure \@ref(fig:discrimination-reason), the most common reason of discrimination within 5 years is sex and ethnicity. In addition, physical appearance, age and language are also typical reasons of discrimination.

@@

@@

>>>>

### 4 Reference\
------------------------------------------------------------------------------------------------10
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)

library(tidyverse)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(here)
library(gridExtra)

source(here::here("scripts/constants.R"))
source(here::here("scripts/cross-compare-barplot.R"))
source(here::here("scripts/cross-compare-plots.R"))
source(here::here("scripts/crime-count.R"))
```

@@

\newpage
# Results

## Classification of Discrimination

The identification of discrimination could be vague and inconsistent in different regions. According to Human rights in Ontario[@humanrights], there are four forms of discrimination: direct, indirect, subtle, and adverse effect discrimination; Harassment; Poisoned environment; Systemic discrimination. Discrimination often derives from different backgrounds and identities. Based on unique combination of identities, people may be exposed to specific forms of discrimination and may experience significant personal harm. The 2014 GSS on Canadians’ Safety and Security (Victimization) mainly captured gender, disability, and ethnicity. It also provides information of the condition when discrimination happens. According to Figure \@ref(fig:discrimination-reason), the most common reason of discrimination within 5 years is sex and ethnicity. In addition, physical appearance, age and language are also typical reasons of discrimination.

@@

```{r crime-plot, echo=FALSE, warning=FALSE, message = FALSE, fig.height=6, fig.width=8}
subset_data = gss_data %>% filter(msvic < 900)  # ignore invalid responses
subset_data %>% 
  left_join(as.data.frame(list(msvic=msvic_num, msvic_label=msvic_labels))) %>%
  ggplot(aes(as.factor(msvic_label), fill=msvic_label)) + geom_histogram(stat="count") + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + xlab("Crime") +
  labs(title = "Crime Count", fill="Crime Category")
```

```{r crime-count-plot-by-education, echo=FALSE, warning=FALSE, message = FALSE, fig.height=6, fig.width=8}
# university_crime_count
grid.arrange(university_crime_count,
            college_crime_count,
            elementary_crime_count,
            nrow=1)
```

@@

# Appendix

# Appendix

```{r sex_crime_plot, echo=FALSE, warning=FALSE, message = FALSE}
sex_crime_plot
```

```{r culture_crime_plot, echo=FALSE, warning=FALSE, message = FALSE}
culture_crime_plot
```

```{r race_skin_crime_plot, echo=FALSE, warning=FALSE, message = FALSE}
race_skin_crime_plot
```

```{r physical_appearance_crime_plot, echo=FALSE, warning=FALSE, message = FALSE}
physical_appearance_crime_plot
```

```{r religion_crime_plot, echo=FALSE, warning=FALSE, message = FALSE}
religion_crime_plot
```

```{r sexual_orientation_crime_plot, echo=FALSE, warning=FALSE, message = FALSE}
sexual_orientation_crime_plot
```

```{r age_crime_plot, echo=FALSE, warning=FALSE, message = FALSE}
age_crime_plot
```

```{r physical_mental_disability_crime_plot, echo=FALSE, warning=FALSE, message = FALSE}
physical_mental_disability_crime_plot
```

```{r language_crime_plot, echo=FALSE, warning=FALSE, message = FALSE}
language_crime_plot
```

```{r fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message = FALSE}
cross_compare_barplot(data=gss_data,
                      col1 = "eor_01c", col2 = "msvic",
                      col1_num=eor_01c_num, col1_labels=eor_01c_label,
                      col2_num=msvic_num, col2_labels=msvic_labels, 
                      plot_title="University Education VS Crime",
                      plot_subtitle="",
                      plot_xlab="Crime",
                      plot_ylab="Percentage", 
                      plot_fill_lab="University Education")
```

```{r fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message = FALSE}
cross_compare_barplot(data=gss_data %>% filter(msvic < 900) %>% filter(eor_01b < 3),
                      col1 = "eor_01b", col2 = "msvic",
                      col1_num=eor_01b_num, col1_labels=eor_01b_label,
                      col2_num=msvic_num, col2_labels=msvic_labels, 
                      plot_title="College Education VS Crime",
                      plot_subtitle="",
                      plot_xlab="Crime", 
                      plot_ylab="Percentage", 
                      plot_fill_lab="college Education")
```

```{r fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message = FALSE}
cross_compare_barplot(data=gss_data %>% filter(msvic < 900) %>% filter(eor_01a < 3),
                      col1 = "eor_01a", col2 = "msvic",
                      col1_num=eor_01a_num, col1_labels=eor_01a_label,
                      col2_num=msvic_num, col2_labels=msvic_labels, 
                      plot_title="Elementary School Education VS Crime",
                      plot_subtitle="",
                      plot_xlab="Crime", 
                      plot_ylab="Percentage",
                      plot_fill_lab="Elementary School Education")
```

```{r fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message = FALSE}
cross_compare_barplot(data=gss_data %>% filter(msvic < 900) %>% filter(eduf10 < 6),
                            col1 = "edum5", col2 = "msvic",
                      col1_num=eduf10_num, col1_labels=eduf10_labels,
                      col2_num=msvic_num, col2_labels=msvic_labels, 
                      plot_title="Father Education VS Crime", 
                      plot_subtitle="Sex Discrimination has an obvious correlation with Sexual Assault", 
                      plot_xlab="Crime", 
                      plot_ylab="Percentage of Father Education", 
                      plot_fill_lab="Education")
```
